%% The first command in your LaTeX source must be the \documentclass command.
%%
%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[
% twocolumn,
% hf,
]{ceurart}
%
\usepackage{lipsum}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{caption}
\usepackage{graphicx}
%%
%% One can fix some overfulls
% \sloppy

%%
%% end of the preamble, start of the body of the document source.
\begin{document}
	
%%
%% Rights management information.
%% CC-BY is default license.
\copyrightyear{2020}
\copyrightclause{Copyright for this paper by its authors.
	Use permitted under Creative Commons License Attribution 4.0
	International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{The 12th Majorov International Conference on Software Engineering and Computer Systems, 2020, Saint-Petersburg, Russia}

\title{Developing a LSM Tree Time Series Storage Library in Golang}


%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
\author[1]{Nikita Tomilov}[%
orcid=0000-0001-9325-0356,
email=programmer174@icloud.com,
url=https://nikita-tomilov.github.io/,
]
\address[1]{ITMO University, Kronverksky Pr. 49, bldg. A, St. Petersburg, 197101, Russia}

%
%\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Due to the recent growth in popularity of the Internet of Things solutions, the amount of data being captured, stored, and transferred is also significantly increasing. The concept of edge devices allows buffering of the time-series measurement data to help mitigating the network issues. 
One of the options to safely buffer the data on such a device within the currently running application is to use some kind of embedded database. However, those can have poor performance, especially on embedded computers. It may lead to bigger response times, which can be harmful for mission-critical applications. That is why in this paper an alternative solution, which involves the LSM tree data structure, was advised.
The article describes the concept of an LSM tree-based storage for buffering time series data on an edge device within the Golang application. To demonstrate this concept, a GoLSM library was developed. Then, a comparative analysis to a traditional in-application data storage engine SQLite was performed. This research shows that the developed library provides faster data reads and data writes than SQLite as long as the timestamps in the time series data are linearly increasing, which is common for any data logging application.
\end{abstract}

\begin{keywords}
	Time Series \sep
	LSM tree \sep 
	SST \sep 
	Golang	
\end{keywords}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

%
%
%
\input{1-theory}
\input{2-lsm-impl}
\input{3-comparison}
\input{4-conclusion}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{time_series_databases}
Dunning, T., Friedman, E.: Time Series Databases: New Ways to Store and Access Data. O'Reilly Media, CA, USA  (2014)

\bibitem{ind_iot_edge}
B. Chen, J. Wan, A. Celesti, D. Li, H. Abbas and Q. Zhang, "Edge Computing in IoT-Based Manufacturing," in IEEE Communications Magazine, vol. 56, no. 9, pp. 103--109 (2018). \doi{10.1109/MCOM.2018.1701231}

\bibitem{lsm_tree_orig}
O’Neil, P., Cheng, E., Gawlick, D. et al. The log-structured merge-tree (LSM-tree). Acta Informatica 33, 351--385 (1996). \doi{10.1007/s002360050048}

\bibitem{sstable}
Adhikari, M., Kar, S. NoSQL databases. In Handbook of Research on Securing Cloud-Based Databases with Biometric Applications (pp. 109-152). IGI Global. (2015)

\bibitem{btree_google}
BTree implementation for Go, \url{https://github.com/google/btree}. Last accessed 31
Oct 2020

\bibitem{go_benchmark}
Go benchmark documentation, \url{https://golang.org/pkg/testing/}. Last accessed 1
Nov 2020

\end{thebibliography}

\end{document}
